A* with Perfect Heuristic/Potentials in Road Networks

### 2020-08-05 paper/ch_potentials.tex
foo

To compare against related work, we introduce the concept of Oracle-A*.
It has access to a perfect shortest distance array as potential.
The array computation time is unaccounted for, i.e., it is magically filled instantly.
Oracle-A* is not achievable in practice.
However, is a lower bound for every algorithm following out setup.
We experimentally show that CH-Potentials are within a factor two of Oracle-A* and thus every related work.

>>>>

To compare against related work, we introduce the concept of Oracle-A*.
It has access to a perfect shortest distance array with respect to $w_\ell$ as potential.
This is the tightest potential achievable during preprocessing. 
The array computation time is unaccounted for, i.e., it is magically filled instantly.
Oracle-A* is not achievable in practice.
However, is a lower bound for every algorithm following our setup.
We experimentally show that CH-Potentials are within a factor two of Oracle-A* and thus every related work.
